---
title: "ReserachAbstractInterpretations"
author: "Ankit Regmi"
date: "2024-12-05"
output: word_document
---

# Analyzing the Border Crossing Patterns by Measure
```{r}
# Loadingnecessary libraries
library(readr)
library(dplyr)
library(ggplot2)
library(scales)

# Loading the tidy dataset
border_sample <- read_csv("Border_Sample_Tidy.csv")


border_patterns <- border_sample %>%
  group_by(Border, Measure) %>%
  summarise(Total_Value = sum(Value), .groups = 'drop')


ggplot(border_patterns, aes(x = Total_Value, y = Measure, fill = Border)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_log10(labels = comma) +  # Log scale for better visualization
  labs(
    title = "Border Crossing Patterns by Measure and Border",
    x = "Total Crossing Volume (log scale)",
    y = "Measure"
  ) +
  theme_minimal() +
  theme(legend.title = element_text(size = 10))

```

The plot above shows the crossing patterns by measure (type of activity) and border:

US-Canada Border: Dominated by measures like personal vehicle passengers and truck-related activities.
US-Mexico Border: Higher volumes of pedestrians and personal vehicle passengers compared to US-Canada.
This suggests different usage patterns for each border, likely due to geographic, economic, and cultural factors.

# Analyzing Border Crossing Rates Over Time
```{r}

time_trends <- border_sample %>%
  group_by(Year, Border) %>%
  summarise(Total_Value = sum(Value), .groups = 'drop')


ggplot(time_trends, aes(x = Year, y = Total_Value, color = Border)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_y_continuous(labels = comma) +
  labs(
    title = "Border Crossing Rates Over Time",
    x = "Year",
    y = "Total Crossing Volume"
  ) +
  theme_minimal() +
  theme(legend.title = element_text(size = 10))

```

The line chart above illustrates how border crossing rates have changed over time for the U.S.-Canada and U.S.-Mexico borders:

U.S.-Canada Border: A relatively stable pattern, with minor fluctuations over the years.
U.S.-Mexico Border: Displays more variability, with significant peaks and troughs, possibly due to policy changes, economic factors, or seasonal influences.
# Analyzing the Effect of Variables on Border Crossings

```{r}
# Calculating the mean crossing value by Border and Measure
measure_effect <- border_sample %>%
  group_by(Border, Measure) %>%
  summarise(Average_Value = mean(Value), .groups = 'drop')


ggplot(measure_effect, aes(x = Average_Value, y = Measure, fill = Border)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_log10(labels = comma) +  # Log scale for better visualization
  labs(
    title = "Effect of Measure on Border Crossings",
    x = "Average Crossing Volume (log scale)",
    y = "Measure"
  ) +
  theme_minimal() +
  theme(legend.title = element_text(size = 10))

```

The bar chart above shows how different measures (crossing types) impact U.S.-Canada and U.S.-Mexico border crossings:

U.S.-Canada Border: Higher average volumes for truck-related activities, indicating the prominence of trade and freight transport.
U.S.-Mexico Border: Higher pedestrian and personal vehicle passenger activity, suggesting a focus on individual and commuter crossings.
